---
title: "Google Drive Function Tutorial Draft 1"
output: html_document
date: "2023-06-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Using googledrive Package

Installing the googledrive package so that it can be used in this project.

```{r Eval = FALSE}
# Installing googledrive
library(googledrive)
```

```{r, include = FALSE}
# Authorization of gmail to be used in project
drive_auth(email = "jcuzziere@gmail.com")
```

# `Drive_Create Function`

## Arguments Include: 
- "Name" = Naming New Files, Documents, Sheets, and Folders. 
- "Path" = Targets Destination for New Item. 
- "Type" = Creating New Files, Documents, Sheets, and Folders. 
- "Overwrite" = Check for Pre-Exhisting File at the targeted filepath.

Creating a **new** folder and a **new** spreadsheet within that folder using `drive_create` function. This new folder and spreadsheet will be used as examples for later functions.

#### Function Example

```{r Eval = FALSE}
# Creating new folder ("exfolder") and new Google Sheet ("exsheet") within created folder
exfolder <- drive_mkdir("exfolder/")
drive_create("exsheet", path = exfolder, type = "spreadsheet")
```

# `As_Dribble Function`

## Argument: 
- "X" = A Vector of Drive file Paths, a Vector of File ids, a List of Files Resource Objects, or a Suitable Data Frame

Use function `as_dribble` to convert a file into a "dribble". A dribble is an object used by googledrive to hold Drive file metadata. 

#### Function Example

```{r Eval = FALSE}
# Making previously created folder into a dribble
as_dribble(exfolder)
```

# `Drive_Find Function`

## Arguments Include: 
- "Pattern" = Only the Items Whose Names Match This Expression are Returned
- "Trashed" = Whether to Search Files that are Not in the Trash (trashed = FALSE, the default), Only Files That are in the Trash (trashed = TRUE), or to Search Regardless of Trashed Status (trashed = NA). 
- "N_Max" = Number of Items to be Found. 
- "Shared_Drive" = Anything that Identifies One Specific Shared Drive. 
- "Corpus" = Specifying Which Collections of Items to Search. 

Can find Docs, Files, Folders, or Sheets in Drive using the `drive_find` function. Can filter search by looking at file type or file name. To get a more accurate search, use function `drive_get` to search by file path or by file id. 

#### Function Examples

```{r Eval = FALSE}
# Searching by file type "spreadsheet"
drive_find(type = "spreadsheet")
```

```{r Eval = FALSE}
# Searching by content in name (folder previously created)
drive_find(q = "name contains 'folder'")
```
```{r Eval = FALSE}
drive_find(type = "folder", n_max = 1, trashed = TRUE)

drive_find(type = "presentation", n_max = 2)

drive_find(type = "document", n_max = 3)
```

